### 2013-05-31 trunk/papers/bprheo_r/bprheo.tex
Update bprheo paper 31 May
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1993 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure*}[htpb]
\includegraphics[width=0.245\textwidth]{disc-xy-10k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-180k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-200k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-210k_run1115.png}\\
\includegraphics[width=0.245\textwidth]{disc-xy-400k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-700k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-750k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-2200k_run1115.png}
\caption{Snapshots of BPI disclination network at $\dot{\gamma}=4.88\e{-6}$: 
Depicted is the transition from the quiescent state to flow-induced, intertwined 
helices that undergo a recurring structural transformation. The top row
shows a section of one unit cell for early times 
$t=1\e{4}, 1.8\e{5}, 2.0\e{5}$ and $2.1\e{5}$. The bottom 
pictures on the far left, centre left and centre right 
show the situation at later time steps $t=4.0, 7.0$ and $7.5\e{5}$,
which the system passes for several cycles before it ends up in
an amorphous state (bottom row far right, at time step $t=2.2\e{6}$).}
\label{bp1-low}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.32\textwidth]{disc-365k_run914.png}
\includegraphics[width=0.32\textwidth]{disc-367k_run914.png}
\includegraphics[width=0.32\textwidth]{disc-375k_run914.png}\\
\includegraphics[width=0.32\textwidth]{disc-380k_run914.png}
\includegraphics[width=0.32\textwidth]{disc-384k_run914.png}
\includegraphics[width=0.32\textwidth]{disc-389k_run914.png}
\caption{Disclination network of BPI in regime BPI-2 (intermediate flow rates): 
The sequence shows a typical cycle of shear-induced transformations in the 
steady state at $\gd=1.56\e{-4}$ and time steps 
$t=3.65, 3.67,3.75,3.80,3.84,3.89\e{5}$ with the flow into/out of the page. 
During every cycle the network is displaced also along the gradient and vorticity direction, 
but the magnitude and direction of the offset does not appear to obey a 
simple rule.}
\label{bp1-med}
\end{figure*}

\begin{figure*}[htpb]
\includegraphics[width=0.495\textwidth]{v_yz-v_z-360k_run914.png}
\includegraphics[width=0.495\textwidth]{v_yz-v_z-360k_run922.png}
\caption{Velocity patterns in BPI for positive (left) and negative (right) helicity: 
The pictures show a snapshot of the periodically recurring patterns in the 
secondary velocity components $(v_y,v_z)$. 
The colour code gives the magnitude and sign 
of the $z$-component. The vertical and horizontal direction are the gradient and 
vorticity direction, respectively, with the flow into/out of the plane in the 
upper/lower half of the images.}
\label{bp1-velo}
\end{figure*}

@@

\begin{figure}[htpb]
\includegraphics[width=0.45\textwidth]{dir3d-z-302k_run916.png}
\caption{Director field of BPI at high shear rate: The pictures show a region 
of $L_x\times L_y \times L_z= 32^3$ lattice sites with the flow/gradient 
direction oriented along the horizontal/vertical axis. 
The colour code gives the magnitude of the z-component of the director field. 
The data show that the structure is quasi-2D, with rolling double twist
patterns in the $xy$ plane, and an approximate translational symmetry 
along the vorticity direction.}
\label{bp1-high}
\end{figure}

>>>>

\begin{figure*}[htpb]
\includegraphics[width=0.245\textwidth]{disc-xy-10k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-180k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-200k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-210k_run1115r.png}\\
\includegraphics[width=0.245\textwidth]{disc-xy-1650k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-1800k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-2000k_run1115r.png}
\includegraphics[width=0.245\textwidth]{disc-xy-2400k_run1115r.png}
\caption{Snapshots of BPI disclination network at $\dot{\gamma}=4.88\e{-6}$: 
Depicted is the transition from the quiescent state to flow-induced, intertwined 
helices that undergo a recurring structural transformation. The top row
shows a section of one unit cell for early times 
$t=1\e{4}, 1.8\e{5}, 2.0\e{5}$ and $2.1\e{5}$. The bottom 
pictures on the far left, centre left and centre right 
show the situation at later time steps $t=1.65, 1.8$ and $2.0\e{6}$,
which the system passes for several cycles before it ends up in
an amorphous state (bottom row far right, at time step $t=2.4\e{6}$).}
\label{bp1-low}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.32\textwidth]{disc-364k_run914r.png}
\includegraphics[width=0.32\textwidth]{disc-366k_run914r.png}
\includegraphics[width=0.32\textwidth]{disc-368k_run914r.png}\\
\includegraphics[width=0.32\textwidth]{disc-370k_run914r.png}
\includegraphics[width=0.32\textwidth]{disc-372k_run914r.png}
\includegraphics[width=0.32\textwidth]{disc-374k_run914r.png}
\caption{Disclination network of BPI in regime BPI-2 (intermediate flow rates): 
The sequence shows a typical cycle of shear-induced transformations in the 
steady state at $\gd=1.56\e{-4}$ and time steps 
$t=3.64, 3.66,3.68,3.70,3.72,3.74\e{5}$ in flow-gradient plane. 
During every cycle the network is displaced also along the gradient and vorticity direction.}
\label{bp1-med}
\end{figure*}

\begin{figure*}[htpb]
\includegraphics[width=0.32\textwidth]{v_yz-v_z-364k_run914r.png}
\includegraphics[width=0.32\textwidth]{v_yz-v_z-366k_run914r.png}
\includegraphics[width=0.32\textwidth]{v_yz-v_z-368k_run914r.png}
\includegraphics[width=0.32\textwidth]{v_yz-v_z-370k_run914r.png}
\includegraphics[width=0.32\textwidth]{v_yz-v_z-372k_run914r.png}
\includegraphics[width=0.32\textwidth]{v_yz-v_z-374k_run914r.png}
\caption{Velocity patterns in BPI for positive helicity: 
The pictures show a snapshot of the periodically recurring patterns in the 
secondary velocity components $(v_y,v_z)$ at $\gd=1.56\e{-4}$ and time steps 
$t=3.64, 3.66,3.68,3.70,3.72,3.74\e{5}$, i.e. for the same shear rate
and time steps as in Fig.\ref{bp1-med}. The colour code gives the magnitude and sign 
of the $z$-component. For negative helicity the sense of motion of the 
network and the secondary velocity components are inversed just as in Fig. \ref{bp2-velo}. 
Note that the viewing direction has been adapted in
each snapshot to give the clearest view on the band-like pattern between
the disclination lines.}
\label{bp1-velo}
\end{figure*}

@@

%\begin{figure}[htpb]
%\includegraphics[width=0.45\textwidth]{dir3d-z-302k_run916.png}
%\caption{Director field of BPI at high shear rate: The pictures show a region 
%of $L_x\times L_y \times L_z= 32^3$ lattice sites with the flow/gradient 
%direction oriented along the horizontal/vertical axis. 
%The colour code gives the magnitude of the z-component of the director field. 
%The data show that the structure is quasi-2D, with rolling double twist
%patterns in the $xy$ plane, and an approximate translational symmetry 
%along the vorticity direction.}
%\label{bp1-high}
%\end{figure}
